Comparison and Evaluation of Popular Syntax Highlighting Themes in Terms of Color Correlated Temperature Values

### 2022-04-23 doc/manuscript.tex
.

In syntax coloring, each syntax group (e.g., an identifier, a keyword) in the source code is displayed with the font selected in color set in the theme. To calculate the contribution of a character in the group to the color temperature, it is necessary to calculate the character bit density from the bitmap of the character in the selected font. To explain the method followed in making this calculation, for example, the definition of BDF given in Figure \ref{code:letter_A_BDF} with the Consolas font of the character \texttt{A} is discussed.

In this definition, each line starting with \texttt{BITMAP} corresponds to a line in the bit matrix of the corresponding
character. A bitmap is obtained when bit patterns reported in hexadecimal are converted to binary (Figure
\ref{fig:letter_A_bitmap}). Based on this bitmap, the appearance of character A is shown in Figure \ref{fig:letter_A}.

@@

\begin{figure}[htbp]
  \caption{BDF definition of the Consolas font for the character '\texttt{a}'}
  \label{code:letter_A_BDF}

@@

\begin{figure}[htbp]
  \caption{Bit pattern in Consolas font of character '\texttt{a}'}
  \label{fig:letter_A_bitmap}

@@

\begin{comment}
Considering the bit pattern at Figure \ref{fig:letter_A_bitmap} "Character bit density" is calculated  as follows.

>>>>

In syntax coloring, each syntax group (e.g., an identifier, a keyword) in the source code is displayed with the font
selected in color set in the theme. To calculate the contribution of a character in the group to the color temperature,
it is necessary to calculate the character bit density from the bitmap of the character in the selected font. To explain
the method followed in making this calculation, for example, the definition of BDF given in Figure
\ref{code:letter_a_BDF} with the Consolas font of the character '\texttt{a}` is discussed.

In this definition, each line starting with \texttt{BITMAP} corresponds to a line in the bit matrix of the corresponding
character. A bitmap is obtained when bit patterns reported in hexadecimal are converted to binary (Figure
\ref{fig:letter_a_bitmap}). Based on this bitmap, the appearance of character '\texttt{a}' is shown in Figure \ref{fig:letter_a}.

@@

\begin{figure}[htbp]
  \caption{BDF definition of the Consolas font for the character '\texttt{a}'}
  \label{code:letter_a_BDF}

@@

\begin{figure}[htbp]
  \caption{Bit pattern in Consolas font of character '\texttt{a}'}
  \label{fig:letter_a_bitmap}

@@

\begin{comment}
Considering the bit pattern at Figure \ref{fig:letter_a_bitmap} "Character bit density" is calculated  as follows.
